### 2022-03-18 sections/introduction.tex
update Luca's comments

However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ if considering beyond the SM processes. Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,

@@

The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.

@@

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
%Compared with previous searches, 
The search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}. 
CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
their full Run 2 data and  set observed(expected) upper limits on  $\BR(t\to cH)$ of $9.4\times10^{-4}(8.6\times10^{-4})$
and $\BR{B}(t\to uH)$ of $7.9\times10^{-4}(1.1\times10^{-3})$~\cite{CMS:2021gfa}.
%CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data. Each limit is obtained assuming the other branching ratio is 0}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{1}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ and tau decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$).
The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to hadrons \nu_{\tau}$ are referred as $\thad$.
The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only in $\thadhad$ final state when the top decay leptonically ($t_{\ell}$) in order to avoid overlap with
multilepton analysis~\cite{Aaboud:2018pob}. 
Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon are named leptonic channels. More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background are implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

>>>>

However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when considering beyond the SM processes. Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,

@@

The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.

@@

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
%Compared with previous searches, 
The search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}. 
CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
the full Run 2 data. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
and are $7.9\times10^{-4}(1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
%CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data. Each limit is obtained assuming the other branching ratio is null.}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{1}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis reported here targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The dataset is divided into several final states depending on the production mode and
the  $W$ and tau decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$).
The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to hadrons \nu_{\tau}$ are referred as $\thad$.
The contribution of 
$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
in $t_h$ when the $\tau$ decays hadronically.
%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
when the top decay leptonically ($t_{\ell}$) in order to avoid overlaps with
other ATLAS searches~\cite{Aaboud:2018pob}. 
Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels. Events with at least one \tauhad with an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are named leptonic channels. More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
fake estimations from multi-jet background is implemented.
% and more
%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

### 2022-03-18 sections/simulated_samples.tex
adding Attilio's comments for CONF note
update Luca's comments

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
in combination with the A14 tune.
%and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
%hadronisation, and the underlying event with the A14 tune.
Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as benchmark.

@@

Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
The contribution of $tH$ associated production is also considered as part of SM Higgs background.
The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
The contribution of triboson production is found to be small and negligible.

@@

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators at which the matrix-element calculation (ME) at the leading or the next-leading order (Order), 
the parton shower model (PS), and the parton distribution function set (PDF) used for the main signal and background samples.}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline

>>>>

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event are modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
in combination with the A14 tune.
%and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
%hadronisation, and the underlying event with the A14 tune.
Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as benchmark.

@@

Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
The contribution of $tH$ associated production is also considered as part of SM Higgs background.
The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
The contribution of triboson production is found to be negligible.

@@

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators used for the main signal and background samples. including the matrix element (ME),
  %at the leading or the next-leading order (Order), 
parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}%  used for the main signal and background samples.}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline

### 2022-03-18 sections/strategy_Htautau.tex
update Luca's comments

\begin{table}
\centering
\caption{Overview of the signal regions (SR), validation region (VR), and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels. Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavour jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
VR &$t_{\ell}\thadhad$-SS     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ SS\\ \hline
\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a high $\pt$ jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
%There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
%is considered as the $q$-jet 
Events should contain 4 jets, with the one at the smallest angular distance to the visible decay of the di-tau being labelled as the q-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
These kinds of events will fall into $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematic fit and collinear approximation for the tau decay products.
The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from the MC simulation
of the $tqH$ signals, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

>>>>

\begin{table}
\centering
\caption{Overview of the signal regions (SR), validation region (VR), and $t\bar{t}$ control regions (CRtt) used for the fake tau scale factor derivation in the leptonic channels. Leptons are required to have either same-sign (SS) or opposite-sign (OS) in each region.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavour jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
VR &$t_{\ell}\thadhad$-SS     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ SS\\ \hline
\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a high $\pt$ jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
%There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
%is considered as the $q$-jet 
Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled as  q-jet since the FCNC top decay products are likely boosted closer together. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
These kinds of events will fall into the $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from a fit of the mass
distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.
